\section{Introduction}

We consider Broadcast Networks of Register Automata (BNRA), a model for networks of agents communicating by broadcast. These systems are composed of an arbitrarily large number of agents whose behavior is specified with a finite automaton equipped with a finite set of private registers. The registers of the agents contain values from an infinite set (represented by natural numbers); initially, agents have distinct values in their registers, so that one could think of these values as identifiers. An agent may send messages of the form of a symbol from a finite alphabet along with the value of one of its registers. No assumption is made on the evolution of the communication graph, \emph{i.e.}, when an agents broadcasts a message, any subset of the other agents may receive it; this is meant to model unreliable systems with unexpected crashes and disconnections. Upon reception of a message, an agent may store the received value in one of its registers or test it for equality with one of its own values. 
This allows an agent, for instance, to check that a sequence of messages all come from the same agent; the broadcasting agent signs messages with its identifier, and the receiving agent stores this identifier then checks that all incoming messages have this value. This also allows an agent to obtain acknowledgement that its message was received by someone, by broadcasting with its identifier and waiting for a response with that same identifier.

This model was introduced in \cite{DelzannoST13}, as a natural extension of Reconfigurable Broadcast Networks~\cite{DelzannoSZ2010Adhoc}. That first paper claimed that the coverability problem, i.e., the problem of whether there is a run from an initial configuration to one where at least one agent is in a designated state, was decidable and even \PSPACE-complete, but the proof turned out to be wrong. As we will see, the complexity of that problem is in fact much higher.

In this paper we establish the decidability of the coverability problem. We even prove its completeness for the hyper-Ackermannian complexity class $\Fcomplexity{\omega^\omega}$, thereby showing that the problem requires a non-multiply recursive amount of time. In fact, this problem is as hard as reachability for lossy channel systems, transition systems with a finite automaton that can store some letters in an unreliable FIFO memory, in which any letter may be erased at any time \cite{AbdullaJ1996verif, Schnoebelen2002verifying,ChambartS08ordinal}. 
We further establish that this problem lies at the frontier of decidability by showing undecidability of the target problem (where one asks whether there is a run at the end of which all agents are in a given state); we contrast these results with the \NP-completeness of the coverability problem when each agent has only one register. 

\textbf{Related work} 
Broadcast protocols are a widely studied class of systems, in which processes are represented by nodes of a graph and can send messages to their neighbors. There are however many choices to make when designing a model for those systems: how individual processes are represented, whether the number of communication graph is fixed or can change, the type of messages they can send... 
A model where messages ranged over a finite alphabet was presented in~\cite{emerson1998model}, over a fully connected communication graph. It was rapidly shown that many basic problems were undecidable over that model~\cite{EsparzaFM1999verification}; similar negatives result were found for Ad Hoc networks where the communication graph is fixed but arbitrary \cite{DBLP:conf/concur/DelzannoSZ10}, lead the community to consider Reconfigurable Broadcast Networks (RBN) where each broadcast can be received by an arbitrary subset of agents~\cite{DelzannoSZ2010Adhoc}.

The complexity of parameterized verification problems over RBN have been the subject of an extensive study in recent years~\cite{DelzannoSTZ12, Balasubramanian18, BalasubramanianGW22, DBLP:journals/computing/ChiniMS22}. In~\cite{DelzannoST13}, RBN were extended to BNRA, the model studied in this article, by the addition of registers allowing processes to exchange identifiers. It is inspired by the success of register automata, which offer a convenient formalism to express properties of words over an infinite alphabet; see~\cite{Segoufin06} for a survey on the subject. \nico{je connais pas et je vois pas le rapport là comme ça?}

Other approaches exist to define parameterized models with registers~\cite{BolligRS21}, such as dynamic register automata in which processes are allowed to spawn other processes with new identifiers and communicate integers values~\cite{AbdullaAKR14}. While basic problems on these models are in general undecidable, some restrictions on communications allow to recover decidability~\cite{AbdullaAKR15, Rezine17}. \nico{on peut enlever ce paragraphe non?}

Such parameterized verification problems often relate to the theory of well quasi-orders and well-structured transition systems, and the associated high complexities obtained from bounds on so-called ``bad sequences'' in ordered sets. In particular, our model is linked to two classical models from this field. The first one is data nets, which are Petri nets in which tokens are labelled with natural numbers, and can exchange and compare their labels~\cite{LazicNORW08}. In general, inequality tests are allowed, but data nets with only equality tests have also been studied~\cite{Rosa-Velardo17}. They do not subsume BNRA as processes can only carry one integer, and not several register values (problems on models of data nets where tokens have tuples of integers as labels are typically undecidable).
The other closely related model is lossy channel systems (LCS)\cite{AbdullaJ1996verif}, which we will simulate using BNRA. We will show that BNRA coverability and LCS reachability are complete for the same complexity class $\Fcomplexity{\omega^\omega}$~\cite{ChambartS08ordinal, Schnoebelen2002verifying}.
\nico{truc mis en commentaire}% As a matter of fact, LCS are derived from distributed models with processes communicating through pairwise channels, which are a rich field of study on their own~\cite{Aiswarya2015model,Aiswarya2020networks}.

\textbf{Overview}
We start with the model definition and some preliminary results in Section~\ref{sec:preliminaries}. We prove decidability of the coverability problem as well as undecidability of the target problem in Section~\ref{sec:cover-decidability}. 
% starting with some basic definitions in Section~\ref{sec:decidability-set-up}, then presenting a sound and complete abstraction, unfolding trees, in~\ref{sec:decidability-tree-unfoldings}, and bounding the size of witnesses in that abstraction in Sections~\ref{sec:tree-bounds}. We establish the coverability decidability theorem in Section~\ref{sec:decidability-end} and the undecidability of a closely-related problem in Section~\ref{sec:undec-target}. 
Finally, we prove the \NP-completeness of the coverability problem with one register per process in Section~\ref{sec:cover-1BNRA}.
Due to space constraints, most proofs are postponed to the appendix.

%
%	\textbf{Broadcast protocols}
%
%	\cite{emerson1998model} -> Introduction of broadcast protocols (no reconfiguration, reliable broadcasts)
%	
%	\cite{EsparzaFM1999verification} -> Undecidability of liveness and safety for this model
%
%	\textbf{Ad hoc Networks}
%
%	\cite{Godskesen2007calculus}, \cite{Merro2007observational} -> From Arnaud's paper
%
%	\textbf{RBN}
%	
%	\cite{DelzannoSZ2010Adhoc} -> Parametrized Model for Ad Hoc networks (undecidable), then switch to RBN
%	
%	\cite{Delzanno2012complexity} -> Complexity of RBN
%	
%	\cite{BouyerMRSS2016} -> ASMS almost-sure reachability
%	
%	\cite{fortin2017model} -> ASMS with stacks and leaders
%	
%	\cite{BalaW2021} -> Equivalence ASMS <-> RBN
%	
%	And some more ! \cite{BalasubramanianBM2018parameterized}, \cite{BalasubramanianGW2022parameterized}, 	\cite{ChiniMS2019liveness} 
%	
%	\textbf{Lossy channel systems}
%	
%	\cite{AbdullaJ1996verif} -> Introduction of LCS
%	
%	\cite{AbdullaJ1996undec} -> Büchi conditions are undecidable for LCS 
%	
%	\cite{SchmitzS2011upperHigman} -> Upper bounds for Higman's lemma
%	
%	\cite{ChambartS2008ordinal} -> Upper bound for LCS coverability 
%	
%	\cite{Schnoebelen2002verifying} -> Lower bound for LCS coverability 
%	
%%
%%	\textbf{Register automata}
%%	
%%%	\cite{kaminski1994finite} -> Introduction of register automata
%%	
%%	\cite{segoufin2006automata} -> survey of results for register automata (didn't find anything more recent)
%%	
%	\textbf{Data nets}
%	
%	\cite{lazic2007nets} -> Introduction of data nets
%	
%	\cite{ROSAVELARDO201741} -> Unordered data nets in $F_{\omega^\omega}$
%	
%	\textbf{Systems communicating via (lossy) channels}
%	
%	\cite{Aiswarya2021network} -> Survey, with some relevant papers 	\cite{Aiswarya2015model},
%	\cite{AbdullaAA2016data}
%
%	\cite{BRS21} -> not really register automata, but systems where each agent has a private register and there are as many shared registers as agents; an agent may change its local value, write it in the global memory and test the number of occurrences of its values. Control-state reachability is \PSPACE-complete.
	
%	\cortoin{J'ai pris les refs de Scholar, mais il vaut mieux les refaire depuis DBLP}