\documentclass[runningheads]{llncs}


\input{General-preamble} 
\input{kl}
\bibliographystyle{splncs04}
\begin{document}
\title{Parameterized Broadcast Networks with Registers: from NP to the Frontiers of Decidability\thanks{\footnotesize{Partly supported by ANR project PAVEDYS (ANR-23-CE48-0005).}}}


\titlerunning{Parameterized broadcast networks with registers} %TODO optional, please use if title is longer than one line

%\author{Jane {Open Access}}{Dummy University Computing Laboratory, [optional: Address], Country \and My second affiliation, Country \and \url{http://www.myhomepage.edu} }{johnqpublic@dummyuni.org}{https://orcid.org/0000-0002-1825-0097}{(Optional) author-specific funding acknowledgements}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional. Use additional curly braces to indicate the correct name splitting when the last name consists of multiple name parts.

%\author{Joan R. Public\footnote{Optional footnote, e.g. to mark corresponding author}}{Department of Informatics, Dummy College, [optional: Address], Country}{joanrpublic@dummycollege.org}{[orcid]}{[funding]}

\author{Lucie Guillou\inst{1} \and Corto Mascle\inst{2} \and Nicolas Waldburger\inst{3}}

\institute{IRIF, CNRS, Université Paris Cité \and 
LaBRI, Université de Bordeaux \and 
IRISA, Universit\'e de Rennes}
\authorrunning{L. Guillou, C. Mascle, N. Waldburger} 


% \Copyright{Lucie Guillou, Corto Mascle and Nicolas Waldburger} 

% \ccsdesc[500]{Theory of computation~Verification by model checking}
% \ccsdesc[300]{Theory of computation~Distributed computing models}

	\maketitle 
	


\newcommand{\cortoin}[1]{\todo[color=blue!20,inline]{\small #1}}
\newcommand{\corto}[1]{\todo[color=blue!20]{\small #1}}

\newcommand{\nicoin}[1]{\todo[color=red!20,inline]{\small #1}}
\newcommand{\nico}[1]{\todo[color=red!20]{\small #1}}

\newcommand{\luin}[1]{\todo[color=teal!20,inline]{\small #1}}
\newcommand{\lu}[1]{\todo[color=teal!20]{\small #1}}

\newif\ifproofs
\proofstrue

\newif\ifintuition
\intuitionfalse

\newif\ifbasic
\basicfalse


% just a first idea

	
	% \begin{abstract}
	% 	We consider the parameterized verification of a model representing an arbitrarily large network of agents which communicate by broadcasting and receiving messages. The broadcast topology is reconfigurable, hence a message sent may be received by any set of agents.
	% 	Agents have local registers which contain identifiers. They may broadcast, receive, store and compare these values using their registers.
	% 	We consider the coverability problem, where one asks whether a given state of the system may be reached by at least one agent. We show that this problem is decidable; however, it is as hard as coverability in lossy channel systems, which is non-primitive recursive. 
	% 	We also consider other classical problems on such systems, in particular the target problem where all processes must synchronize on a given state. This problem is however undecidable for our model. 
	% 	By contrast, we prove that the coverability problem is \NP-complete when each agent has only one register.
		
	% 	\keywords{Parameterized verification \and Well quasi-orders \and Distributed systems }
	% \end{abstract}
%	
%Reconfigurable broadcast networks (RBN) are a well-studied model of distributed systems with arbitrarily many agents communicating by (unreliable) broadcast. In this talk we will study a version of RBN where agents have local registers. Register values are initially all distinct and may therefore be thought of as identifiers.
%When an agent broadcasts a message, it appends to it the value stored in one of its registers. Upon reception, an agent can store the received value or test this value for equality with one of its own registers.
%We consider the coverability problem (whether some state q may be reached by at least one agent) for this model. We establish that this problem is decidable, by reasoning about parallelism and transition systems with registers to be able to leverage well quasi-order theory.
%


	\begin{abstract}
	We consider the parameterized verification of networks of agents which communicate through unreliable broadcasts. In this model, agents have local registers whose values are unordered and initially distinct and may therefore be thought of as identifiers.
	When an agent broadcasts a message, it appends to the message the value stored in one of its registers. 
	Upon reception, an agent can store the received value or test it for equality against one of its own registers. 
	We consider the coverability problem, where one asks whether a given state of the system may be reached by at least one agent. We establish that this problem is decidable, although non-primitive recursive. We contrast this with the undecidability of the closely related target problem where all agents must synchronize on a given state. 
	On the other hand, we show that the coverability problem is \NP-complete when each agent only has one register.
	
	\keywords{Parameterized verification \and Well quasi-orders \and Distributed systems }
	 
	\end{abstract}


	\input{Intro}
		\paragraph*{}
	In this document, occurrences of notions are linked to the definitions of the notions using the \href{https://www.irif.fr/~colcombe/knowledge_en.html}{knowledge package}. On electronic devices, clicking on words or symbols allows to access their definitions.
	
%\input{todo}
	\input{General-defs}
	\input{General-abstraction}
	\input{General-target}
	\section{Cover in 1-BNRA}
	\label{sec:cover-1BNRA}
	\input{defs}
	\input{abstraction}
%	
%\input{Figures/zoom-on-tree}
	\section{Conclusion}
	We established the decidability (and $\Fcomplexity{\omega^\omega}$-completeness) of the coverability problem for BNRA, as well as the \NP-completeness of the problem for 1-BNRA.
	Concerning future work, one may want to push decidability further, for instance by enriching our protocols
	with inequality tests, as done in classical models such as data nets  \cite{datanetsinequalityfomegaomegaomega}. 
	Reductions of other distributed models to this one are also being studied.
	
	\paragraph*{Acknowledgements.} We are grateful to Arnaud Sangnier for encouraging us to work on BNRA, for the discussions about his work in \cite{DelzannoST13} and for his valuable advice. We also thank Philippe Schnoebelen for the interesting discussion and Sylvain Schmitz for the exchange on complexity class $\Fcomplexity{\omega^{\omega}}$ and related topics.   
	\bibliography{biblio}
	
	\newpage
	
	\appendix
%	\input{Appendix/Preuve-simple-protocols}
	\input{Appendix/Preuve-LCS-reduction} 
	\input{Appendix/definition-unfolding-trees}
	\input{Appendix/Preuve-trees-sound-complete}

	\input{Appendix/Preuves-reductions-branches}
	\input{Appendix/Preuve-Tower-lemma}
	\input{Appendix/Preuves-tree-bounds}
	\input{Appendix/decidability}
	\input{Appendix/Preuve-Target}
	\input{Appendix/one-reg-proofs-v3}
\end{document}