% !TeX root = main.tex
\documentclass{beamer}
\usetheme{Copenhagen}
%\usecolortheme{whale}
\setbeamertemplate{itemize item}[triangle]
\setbeamertemplate{itemize subitem}[square]
\useoutertheme{infolines}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{comment}
\usepackage{appendixnumberbeamer}
\usetikzlibrary{arrows, arrows.meta,calc,automata,fit,shapes,positioning}
\tikzset{AUT style/.style={>=angle 60,initial text= ,every edge/.append,every state/.style={minimum size=20,inner sep=2}}}

\definecolor{RealGreen}{HTML}{33bb33}
\definecolor{DarkGreen}{HTML}{338833}

\newcommand{\messages}{\mathcal{M}}
\newcommand{\br}{\mathbf{br}}
\newcommand{\rec}{\mathbf{rec}}
\newcommand{\reg}{\hspace{-0.5mm}\square}
%
%\setbeamertemplate{section in toc}[square]
\setbeamercolor{section number projected}{bg=black,fg=white}

\begin{document}
	
	\title[]{Parameterized verification of Broadcast networks of Register automata}
	\date[]{January 16th, 2024}
	\author[Nicolas Waldburger]{Nicolas Waldburger\\ joint work with Lucie Guillou and Corto Mascle}
	\institute[]{ANR PaVeDyS}
	\setbeamertemplate{navigation symbols}{}
	\addtobeamertemplate{title page}{}{\begin{center}{To be published at FoSSaCS'24}\end{center}}
%	
\begin{frame}
	\titlepage
\end{frame}	

\begin{frame}
	\tableofcontents
\end{frame}

\section{Broadcast networks}

\subsection{Basic model}

\begin{frame}
	\tableofcontents[currentsection]
\end{frame}


\begin{frame}{Broadcast networks}
	\centering
	\input{Figures/RBN-protocol}
\end{frame}


\begin{frame}{Broadcast networks}
	\centering
	\input{Figures/RBN-example}
\end{frame}

\begin{frame}{Broadcast Networks}
	\begin{block}{Definition$^1$}
		(Reconfigurable) Broadcast Network = $(Q, M, \Delta, q_0)$ with $\Delta \subseteq Q\times \{\mathbf{br}(m), \mathbf{rec}(m) \mid m \in M\} \times Q$.
	\end{block}
	
	\pause
	
	\begin{itemize}
		\item Arbitrarily many agents at the start
		
		\item One step = an agent broadcasts a message $m$,\\ some (arbitrary subset of) other agents receive it.
	\end{itemize}
	
	\pause 
	
	\begin{block}{Problems}
%		\vspace{0.3cm}
		{\sc{Cover}}: Is there a run in which \textbf{an} agent reaches \color{blue!60}$q_f$\color{black}?
%		\vspace{0.3cm}
		
		{\sc{Target}}: Is there a run in which \textbf{all agents} reach \color{blue!60}$q_f~$\color{black} \textbf{simultaneously}?
	\end{block}
	
	Both problems are decidable in PTIME\footnote<3>{Delzanno, Sangnier, Zavattaro, CONCUR'10}\footnote<3>{Fournier, PhD thesis, 2015}.
\end{frame}

\subsection{With registers}

\begin{frame}
	\tableofcontents[currentsubsection]
\end{frame}

\begin{frame}{Registers}
	
	Each agent now has local registers $\reg_1, \ldots, \reg_r$, containing values in $\mathbb{N}$.\vspace{0.3cm}\pause
	
	\input{Figures/BNRA-protocol}
\end{frame}

\begin{frame}{Broadcast Networks of Register Automata (BNRA)\footnote{Delzanno, Sangnier, Traverso, RP'13}}
	Each agent now has local \emph{registers} $\reg_1, \ldots, \reg_r$, containing values in $\mathbb{N}$.
	\pause
	\textbf{Initially, all registers of all agents contain distinct values.}
	
	\pause
	\vspace{0.2cm}
	Messages also contain values: $(m, v) \in M\times \mathbb{N}$.
	An agent can:
	\begin{itemize}
		\item Broadcast a message with a register value $\mathbf{br}(m, r_i)$\vspace{0.3cm}\pause
		
%		\item Test equality between its registers $\mathbf{loc}(r_i, r_j, =), \mathbf{loc}(r_i, r_j, \neq)$\pause
		
		\item Receive messages $\mathbf{rec}(m, r_i, op)$, with $op$ either
		\begin{itemize}
			\item store the value $\downarrow$,
			
			\item test it for equality $=, \neq$
			
			\item or do nothing $*$.
		\end{itemize}   
	\end{itemize}

	\pause

	\emph{Remark}: the model where one allows to send two messages per broadcast is undecidable$^3$.
\end{frame}

\begin{frame}{Things we can do}
	
	We can check that a sequence of messages all come from the same agent.

	\begin{center}
	\input{Figures/Predecessor-protocol}
	\end{center}
\end{frame}

\begin{frame}{Things we can do}
	We can check that a sequence of messages we sent was received.
	
	\centering
		\input{Figures/Successor-protocol}
\end{frame}

\begin{frame}{Parameterized verification principles}
	
	\begin{itemize}
		\item Unlimited supply of agents.
		
		\item For {\sc{Cover}}, we can add as many agents as we need at no cost. 
	\end{itemize}
	
	\pause
	
	\begin{block}{Copycat principle}
		Given a run $\rho$, we can construct a run made of many copies of $\rho$ running in parallel.
	\end{block}
	
	\begin{block}{Main theorem}
		{\sc{Cover}} is decidable for BNRA.
	\end{block}


\end{frame}







\section{Signature BNRA}

\begin{frame}
	\tableofcontents[currentsection]
\end{frame}

\begin{frame}{Signature BNRA}
	\begin{block}{Signature BNRA}
		An agent never modifies its first register, and only broadcasts with the value of its first signature.
		
		Other registers are used to store and compare values received.
	\end{block}
	The first register acts as an identity with which agents sign their messages. 
	
	\vspace{-0.4cm}
	\begin{center}
		\begin{tikzpicture}
			\draw[red] (0.15,0.15) circle (0.3); 
			%		\node at (-0.2, -0.2) {\scriptsize\color{red} id};
			\node at (0.2, 1) {\scriptsize\color{red} br};
			\draw[purple] (1.3,0.15) ellipse (0.8 and 0.4);
			\node at (1.6, -0.4) {\scriptsize\color{purple} rec};
			\node at (1.8, -0.7) {\scriptsize\color{purple} $\downarrow, =, \neq$};
			
			\draw (0,0) rectangle (0.3,0.3);
			\draw (0.6,0) rectangle (0.9,0.3);
			\node at (1.3,0.15) {$\cdots$};
			\draw (1.6,0) rectangle (1.9,0.3);
			
			\draw[red, arrows = {-Stealth[length=5pt, inset=2pt]}] (0.15, 0.45) .. controls +(0,0.3) and +(0,-0.3) .. (0.5, 1); 
			\draw[purple, arrows = {-Stealth[length=5pt, inset=2pt]}] (1.15, -1) .. controls +(0,0.3) and +(0,-0.3) .. (1.3, -0.25); 
		\end{tikzpicture}
	\end{center}
	
	\pause
	\textbf{\small Messages received with the same value come from the same agent.}
\end{frame}



\subsection{Well quasi-orders}

\begin{frame}
	\tableofcontents[currentsubsection]
\end{frame}


\begin{frame}{Well quasi-orders}
		 
	
		\input{Figures/Rectangle-wqo}
		
		\onslide<1-12>{\onslide<2->{$(4,3)$}\onslide<4>{$\to {\color{red}(6,3)}$}\onslide<5->{\hspace{-1.35cm}$\to (2,4)$}\onslide<6->{$\to (7,1)$}\onslide<7->{$\to (0,5)$}\onslide<8->{$\to (8,0)$}\onslide<9->{$\to (3,1)$}\onslide<10->{$\to (1,2)$}\onslide<11->{$\to (0,0)$}}

\onslide<16->{König's lemma $\to$ this tree is finite. 

In fact, there is a computable bound on the length of the longest branch.
}


\onslide<17>{\textbf{We can enumerate all possible such trees!}}

%	
%\onslide<13>{\input{Figures/Tree-wqo}}
	
%	\vspace{1cm}\onslide<2->{$(4,3)$}\onslide<4>{$\to (4,2)$}\onslide<5->{\hspace{-1.35cm}$\to (2,4)$}\onslide<6->{$\to (7,1)$}\onslide<7->{$\to (0,5)$}\onslide<8->{$\to (8,0)$}\onslide<9->{$\to (3,1)$}\onslide<10->{$\to (1,2)$}\onslide<11->{$\to (0,0)$}
\end{frame}


\begin{frame}{Well quasi-orders: Subwords}
	
	\begin{block}{Higman's lemma}
		For all finite alphabet $\Sigma$, the subword order $\preceq$ is a well quasi-order over $\Sigma^*$.
	\end{block}

	\pause
	$\Leftrightarrow$ Any sequence $w_0, w_1, w_2, \ldots$ of words over $\Sigma$ such that $w_i \npreceq w_j$ for all $i<j$ is \textbf{finite}.
	
	\vspace{1cm}
	\pause
	Given a finite alphabet $\Sigma$ and a computable function $B : \mathbb{N} \to \mathbb{N}$, the set of sequences $(w_i)_{i \in \mathbb{N}}$ over $\Sigma$ such that
	\begin{itemize}
		\item $w_i \npreceq w_j$ for all $i<j$ 
		\item $|w_i| \leq B(i)$ for all $i$
	\end{itemize}
is finite and computable.
\end{frame}

\subsection{Decidability proof}

\begin{frame}
	\tableofcontents[currentsubsection]
\end{frame}

\begin{frame}{Towards a tree abstraction}
Assume that there is a valid run $\rho$ for COVER. 
\begin{block}{Observation 1}
If agent $a$ broadcasts to agents $b$ and $c$, we can make copy agent $a$ so that $b$ and $c$ receive messages from distinct agents. 
\end{block}
We can modify $\rho$ so that each agent sends messages to one single agent.
\pause

\begin{block}{Observation 2}
If $a$ broadcasts $m_1$ to $b$ then $b$ broadcasts $m_2$ to $a$, we can make a copy $a'$ of $a$ that broadcasts to $b$ and then stops; $a' \to b \to a$.
\end{block}
More generally, we can guarantee that the graph of ``who sends messages to whom'' has no cycle: it's a tree (or a forest) !
\end{frame}
	

\begin{frame}{Tree unfoldings}
	

	\input{Figures/Tree-local-runs}
	
\end{frame}

\begin{frame}{Tree unfoldings}
	\input{Figures/Tree-local-runs-full}
	
\end{frame}

\begin{frame}{Branch reduction}
	
	\begin{block}{Lemma}
		If a node labelled $w$ has a descendant labelled $w'$ with $w$ a subword of $w'$ then the tree can be reduced.
	\end{block}
	
	\input{Figures/Branch-reduction}
\end{frame}

\begin{frame}{Branch reduction}
	\begin{itemize}
		\item We can assume that a node labelled $w$ has no descendant labelled $w' \succeq w$.
		\pause 
		\item In order to bound the size of the tree, we need a bound on the growth of the size of the nodes.
	\end{itemize}

	\pause

	\begin{block}{Shortening long local runs} There exists a primitive recursive function $\varphi: \mathbb{N} \rightarrow \mathbb{N}$ such that, if an agent must broadcast $k$ messages, its local run does not need to have more than $k \, \varphi(|\mathcal{P}|)$ steps. 
	\end{block}
	$|\mathcal{P}|$: size of the protocol \\
	Proof by shortening arguments (a bit involved)
\end{frame}

\begin{frame}{Bounding the branches}
	\centering
	\input{Figures/Bound-signature-tree}

\end{frame}


\begin{frame}{Decidability and complexity}
	\begin{block}{Bounds}
	We use the previous argument to bound (in an irreducible tree):
	\begin{itemize}
	\item the length of all branches,
	\item the size of every node,
	\item the maximal degree of the tree.
	\end{itemize}
	This bounds the total space needed to store such a tree.
	\end{block}
	\pause 

	We can enumerate all irreducible trees in finite time, therefore
	
	\begin{block}{Theorem}
		The {\sc{Cover}} problem for \color{blue}signature \color{black} BNRA is decidable \onslide<3->{\color{red!70!black} and in $\mathbf{F}_{\omega^\omega}$.}
	\end{block} 
	\onslide<4->{Can be extended to the non-signature case.} 
\end{frame}

\begin{frame}{Complexity lower bounds}
	\begin{block}{Lossy Channel Systems}
	A \emph{Lossy Channel System} (LCS) is a transition system with a FIFO queue and unreliable writes.
	\end{block}

	\begin{block}{Theorem}
	LCS reachability is $\mathbf{F}_{\omega^\omega}$-hard\footnote{Schnoebelen, Information Processing Letters '08}.
	\end{block}

	\pause 

	\begin{block}{Theorem}
	{\sc{Cover}} in BNRA is $\mathbf{F}_{\omega^\omega}$-complete, even for signature protocols with two registers.
	\end{block}

	\pause
	It is however NP-complete when each agent has only one register.
\end{frame}



% \begin{frame}{Complexity bounds}
	
	
	
% 	\begin{block}{Length function theorem}
% 		For all finite $\Sigma$, for all $g : \mathbb{N} \to \mathbb{N}$ primitive recursive, there exists a function $F : \mathbb{N} \to \mathbb{N}$ of $\mathcal{F}_{\omega^{|\Sigma|-1}}$ such that for all $n \in \mathbb{N}$, every sequence $w_0, w_1, \ldots \in \Sigma^*$ such that $|w_i| \leq g^i(n)$ for all $i$ has at most $F(n)$ terms.\footnote{Cichon, Tahan Bittar, Theoretical Computer Science, '98}\footnote{Schmitz, Schnoebelen, ICALP'11}
% 	\end{block}
	
% 	\begin{itemize}
% 		\item We can bound the tree size by a function of $\mathcal{F}_{\omega^{\omega}}$.
% 	\end{itemize}
	
% %	\begin{block}{Lemma (Lower bound)}
% %		Reachability in Lossy channel systems is $\mathbf{F}_{\omega^\omega}$-complete.
% %	\end{block}
% %	
% %	\begin{itemize}
% %		\item We can encode LCS in BNRA by a PTIME reduction.
% %	\end{itemize}
% 	\pause
% 	\begin{block}{Theorem}
% 		{\sc{Cover}} in BNRA is $\mathbf{F}_{\omega^\omega}$-complete, even for a fixed number of registers $r\geq 2$.
% 	\end{block}
	
% 	\pause
	
% 	\begin{block}{Theorem}
% 		 {\sc{Cover}} in BNRA with one register is $\mathbf{NP}$-complete.
% 	\end{block}
% \end{frame}

\begin{frame}{Conclusion}
% \begin{itemize}
% 	\item Add mustard! \begin{itemize}
% 		\item Pushdown agents
% 		\item Inequality tests $\leq$
% 	\end{itemize} 
		
% 	\item Less permissive communication topology?
	
% 	\item Bounded number of alternations between broadcast and receive?
% \end{itemize} 

	\Huge \textbf{Thank you for your attention!}
\end{frame}

\appendix
 \begin{frame}
  
 \end{frame}
\begin{frame}{Complexity: encoding Lossy Channel Systems}
	Lossy Channel System = Transition system with FIFO memory + unreliable writes.\vspace{1cm}
	
	\input{Figures/LCS-example}
\end{frame}


\begin{frame}{Complexity: encoding Lossy Channel Systems}
	We simulate an LCS through a chain of agents that each apply a transition.
	
	Each agent stores:
	\begin{itemize}
		\item An identifier for itself
		
		\item Its predecessor's identifier
	\end{itemize} 
	
	\input{Figures/LCS-reduction}
	
\end{frame}

\begin{frame}{Complexity: encoding Lossy Channel Systems}
	
	\input{Figures/LCS-transitions}
	
\end{frame}

\begin{frame}{Complexity results}
	
	$\mathbf{F}_{\omega^\omega}$ = Hyper-Ackermannian complexity class.
	
	\begin{block}{Theorem}
		LCS reachability is $\mathbf{F}_{\omega^\omega}$-hard\footnote{Schnoebelen, Information Processing Letters '08}.
	\end{block}
	\pause 

	\begin{block}{Theorem}
		{\sc{Cover}} in BNRA is $\mathbf{F}_{\omega^\omega}$-complete, even for signature protocols with two registers.
	\end{block}
	\pause 

	\begin{block}{Theorem}
		 {\sc{Cover}} in BNRA with one register is $\mathbf{NP}$-complete.
	\end{block}
	
\end{frame}

\end{document}