\section{Proof of Proposition~\ref{prop:trees-sound-complete}}
\label{app:trees-sound-complete}

\treessoundcomplete*
 
We start with a few definitions. 
First, we define the projection of a "run" onto an agent, which corresponds to the intuitive idea that a "local run" is used to describe the point of view of a single agent in a "run". Given a run $\run: \config_0 \step{} \config_1 \step{} \cdots \step{}\config_n$ and a agent $a$, the "local run" $\localrun$ of $a$ in $\run$ is defined by induction. The "local run" of $a$ in the empty run is the empty local run. Let $\localrun_i$ the local run of $a$ in $\config_0 \step{} \config_i$ (prefix of length $i$ of $\run$). We define $\localrun_{i+1}$ as follows:
\begin{itemize}
\item if in $\config_i \step{} \config_{i+1}$, $a$ performs a "local test" or a "broadcast" with a transition $\atrans$ then $u_{i+1}$ is $u_i$ to which a step labeled by $\intstep{\atrans}$ is appended,
\item if in $\config_i \step{} \config_{i+1}$, $a$ performs a "reception" with a transition $\atrans$ then, by letting $\aval$ the value of the message recevied, $u_{i+1}$ is $u_i$ to which a step labeled by $\step{\extlabel{\atrans}{\aval}}$ is appended,
\item if $\config_i \step{} \config_{i+1}$ does not involve $a$, then $u_{i+1} := u_i$.
\end{itemize}

We make the meaning of the "specification" labels more concrete by defining the criteria for a "run" to satisfy a "specification".

\begin{itemize}
	\item A "run" $\run$ satisfies a "boss specification" $\bossspec$ if there exists $\aval \in \nats$ such that $\bossspec$ is a subword of the sequence of messages sent with value $\aval$ in $\run$.
	
	
	\item A "run" $\run$ satisfies a follower specification $(\followwordspec, \followmessagespec)$ if there exists a value $\aval$ and an agent $a$ such that $\aval$ is not an initial value of $a$, the $\aval$-input of $a$ in $\run$ is a subword of $\followwordspec$ and agent $a$ broadcasts $\followmessagespec$ with value $\aval$ at some point.
\end{itemize}

For an "unfolding tree", satisfying a specification simply means that its root is labelled with that specification or a better one.

\begin{itemize}
	\item An "unfolding tree" satisfies a boss specification $\bossspec$ if its root $\node$ is a "boss node" and $\bossspec$ is a subword of its specification label $\bosslabel{\node}$.
	
	\item An "unfolding tree" satisfies a follower specification $(\followwordspec, \followmessagespec)$ if its root $\node$ is a "follower node" such that $\followmessagespec=\followlabelmessage{\node}$ and  $\followlabelword{\node}$ is a subword of $\followwordspec$.
\end{itemize}




% Also note that the interpretation of the "follower nodes" changes between the two directions: when building the tree a follower node labelled $(\followwordspec, \followmessagespec)$ means that there exists a global run in which some agent receives the sequence of messages $\followwordspec$ and broadcasts $\followmessagespec$, all with a value $\aval$ that is not one of its initial ones.

% When building the run a follower node means that there exists a "partial run" which receives a sequence of external messages which forms the word $fw$, with a value $v$ that it initially does not contain, and eventually broadcasts $m$ with that same value.

Note that one can modify the system so that the \COVER problem becomes the problem of the existence of a "run" satisfying a "boss specification"; to do so, it suffices to add a broadcast loop on $q_f$ that broadcasts a special message type. Therefore, it suffices to prove that "runs" of $\prot$ and "unfolding trees" satisfy the same "boss specifications". To do so, we prove the two following implications:

\begin{restatable}{lemma}{LemRunToTree}
	\label{lem:run-to-tree}
	If there exists a "run" $\run$ of $\prot$ satisfying some "specification" $\spec$ then there exists a finite "unfolding tree" $\tree$ over $\prot$ satisfying $\spec$.
\end{restatable}

\begin{restatable}{lemma}{LemTreeToRun}
	\label{lem:tree-to-run}
	If there exists an "unfolding tree" over $\prot$ satisfying a "boss specification" $\bossspec \in \messages^*$ then there exists a finite "run" $\run$ of $\prot$ satisfying $\bossspec$.
\end{restatable}
\input{Appendix/Preuve-run-to-tree}

	\input{Appendix/Preuve-tree-to-run}

