\section{Proof of Lemma~\ref{prop:loc-eq-test-elimination}}
\label{sec:proof-lol-eq-test-elim}

\SimpleReduction*


%old statement to go from local to global, no longer useful 
% \begin{lemma}
% 	\label{lem:local-to-global}
% 	If two protocols $\prot_1, \prot_2$ are such that for all local run $u_1$ of $\prot_1$, there is a local run $u_2$ of $\prot_2$ with the same initial values as $u_1$ and such that $\Input{u_1} = \Input{u_2}$ and $\Output{u_1} = \Output{u_2}$, then for all "boss specification" $bw \in \messages^*$, if $\prot_1$ has a run satisfying $\spec$ then so does $\prot_2$.
% \end{lemma}

% \cortoin{Only useful for the local equality test elimination}
% \ifproofs
% \begin{proof}
% 	We infer this statement from the "unfolding trees".
	
% 	Suppose $\prot_1$ satisfies a specification $\spec$, then by Lemma~\ref{lem:run-to-tree} there exists a "unfolding tree" $\tree_1$ labelled by local runs of $\prot_1$ satisfying $\spec$. 
	
% 	Let $\node$ be a node of $\tree_1$ labelled by a "local run" $u_1$ of $\prot_1$, a value $v$ and a "specification" $\spec$.  
	
% 	There exists a "local run" $u_2$ of $\prot_2$ with the same initial values, "input" and "output" as $u_1$. In particular they have the same $v$-input and $v$-output.
	
% 	We define $\tree_2$ as the tree obtained by replacing in the label of each node the local run of $\prot_1$ by a local run of $\prot_2$ with the same initial values, "input" and "output". The rest of the labels stays the same.
	
% 	Conditions \ref{unfoldingC1}, \ref{unfoldingC2} and \ref{unfoldingC3} are still satisfied on every node as they only talk about the initial values, "input" and "output" of each local run label, and the value and specification labels. None of those things have changed.
% 	Furthermore as the specification label of the root is the same for $\tree_1$ and $\tree_2$, $\tree_2$ satisfies $\spec$.
	
% 	By Lemma~\ref{lem:tree-to-run}, as $\spec$ is a "boss specification", there exists a "run" of $\prot_2$ satisfying $\spec$.
% \end{proof}
% \fi

\begin{proof}
	We construct a "protocol" $\prot'$ with no "local equality tests" so that any "run" of $\prot$ may be turned into an execution of $\prot'$ and vice-versa. 
	The intuition is as followed. $\prot'$ corresponds to $\prot$, where an abstract layer is added in the treatments of the registers. In $\prot'$, we do not directly store each register but rather equality relations between them, so that a value shared by several registers is only stored once. We dub registers of $\prot'$ ""memory slots"" to distinguish them from the registers of $\prot$. A "memory slot" will be used to store a value shared between registers. 
	We will need $\regnum$ "memory slots" to do so. Moreover, we will need a mapping $\map : \nset{1}{r} \to \nset{1}{r}$ that tells, for each "register", in which "memory slot" its value is stored. This mapping will be directly encoded in the set of states of $\prot'$, which causes an exponential blowup in the size of the protocol.
	
	For simplicity, we allow our protocol $\prot'$ to have dummy transitions with no effect (such transitions could be encoded using broadcasts with a dummy message type). 
	
	Let $\prot = (Q, \messages, \transitions', q_0, \regnum)$. 
	We define $\prot' := (Q', \messages, \transitions', q_0', \regnum +1)$ as follows. The set of states is $Q' := Q \times (\nset{1}{r} \to \nset{1}{r})$, its initial state is $q_0' := (q_0, \idmap)$ where $\idmap(i) = i$ for all $i \in \nset{1}{r}$. 
	
	The set of transitions $\transitions'$ is defined as follows.
	For all $q,q' \in Q$ and $\map, \map' \in \nset{1}{r} \to \nset{1}{r}$, we have $((q, \map), \op, (q', \map')) \in \transitions'$ in the following cases:
	
	\begin{itemize}
		\item $\op = \br{m}{j}$, 
		$\map = \map'$ and $(q, \br{m}{i}, q') \in \transitions$ for some $i$ such that $\map(i) = j$ (we broadcast the value stored in the corresponding "memory slot").
		
		\item $\op=\rec{m}{j}{\enregact}$, there is a transition $(q, \rec{m}{i_0}{\enregact}, q') \in \transitions$ with $\map^{-1}(j) \subseteq \set{i_0}$ and for all $i \in \nset{1}{r}$, if $i \ne i_0$ then $\map'(i) = \map(i)$ and $\map'(i_0) = j$ (the received value is stored into a fresh "memory slot").
		
		\item $\op = \rec{m}{j}{\eqtestact}$ and either
		\begin{itemize}
			\item there is a transition $(q, \rec{m}{i}{\eqtestact}, q') \in \transitions$ such that $\map(i)=j$ and $\map'=\map$ (to test equality with register $i$, we test equality with the "memory slot" containing value of register $i$), or
			
			\item there is a transition $(q, \rec{m}{i_0}{\enregact}, q') \in \transitions$ such that $\map'(i_0)=j$ and $\map'(i) = \map(i)$ for every $i \neq i_0$ (register $i_0$ stores a value that is already in a "memory slot" hence we simply modify the mapping).
		\end{itemize} 
		
		\item $\op = \rec{m}{j}{\diseqtestact}$ and there is a transition $(q, \rec{m}{i}{\diseqtestact}, q') \in \transitions$ such that $\map(i)=j$ (to test disequality with register $i$, we test disequality with the "memory slot" containing value of register $i$).
		

		\item $\op=\loc{j_1}{j_2}{\diseqtestact}$ and there is a transition $(q, \loc{i_1}{i_2}{\diseqtestact}, q')$ such that $\map(i_1)=j_1$ and $\map(i_2) = j_2$ (to implement a local disequality test, we do the corresponding test on "memory slots"; this test always fails if $j_1 = j_2$).
		
		
		\item $\op = \rec{m}{j}{\dummyact}$ and there is a transition $(q, \rec{m}{i}{\dummyact}, q') \in \transitions$ for some $i \in \nset{1}{r}$.
	\end{itemize}
	
	Additionally, there is a dummy transition between $(q,\map)$ and $(q',\map')$ whenever there exist $i_1, i_2$ such that $(q, \loc{i_1}{i_2}{\eqtestact}, q') \in \transitions$ and $\map(i_1) = \map(i_2)$ (an equality test on two registers mapped to the same" memory slot" automatically succeeds).

	Note that we cannot in fact guarantee that values stored in the "memory slots" are all distinct, because, upon reception of a value, we may only perform one test and therefore cannot test that the value is different from all stored values. This is why we still need "local disequality tests" in $\prot'$. In practice, when a agent in $\prot$ performs a $\quotemarks{\enregact}$ reception of a broadcast with a value that is already in one of its "memory slots", the corresponding agent in $\prot'$ may non-deterministically notice that it already has this value in a "memory slot" (corresponds to a $\rec{\amessage}{j}{\eqtestact}$ transition) but it may also store it in a fresh "memory slot" (corresponds to a $\rec{\amessage}{j}{\enregact}$ transition). Therefore, the encoding of the content of the registers into a mapping and "memory slots" is not unique, even up to permutation of the memory slots. However, encodings that do not gather together registers with the same value will simply allow less transitions (it will forbid some equality tests), therefore this is not an issue. 

	We now prove that, for a given state $q_f \in Q$, $q_f$ may be covered in $\prot$ if and only if $Q_f' := \set{(q_f, \map) \mid \map \in \nset{1}{r} \to \nset{1}{r}}$ may be covered in $\prot'$. To do so, we will prove that any run of $\prot$ may be turned into a run of $\prot'$ and vice-versa. 
  
	Let $\agents \subseteq \nats$.
	Given a configuration $\config$ of $\prot$, we denote by \AP $\intro*\memoryproj{\config}$ 
	the set of states $\config' \in Q'$ over set of agents $\agents$ such that:
	 for all $a \in \agents$, by denoting $(q, \localdata):= \config(a)$, one has $\config'(a) = ((q, \map), \localdata')$ where, for every $i \in \nset{1}{r}$, $\localdata'(\map(i)) = \localdata(i)$. 
	Moreover, we denote by \AP $\intro*\perfproj{\config}$ 
	the subset of $\memoryproj{\config}$ containing configurations 
	$\config'$ that additionally satisfy that, for every agent, for every $j \ne j' \in \nset{1}{r}$, $\localdata'(j) \ne \localdata(j')$ (we call such configurations ""perfect configurations"" of $\prot'$).

	Let $\run: \config_0 \step{*} \config_f$ a run on $\prot$ over some set of agents $\agents$. We prove by induction on the length of $\run$ that there exists a run $\run': \config_0' \step{*} \config_f'$ on $\prot'$ such that $\config_f' \in \perfproj{\config_f}$. This property is trivially true for $\run$ of length $0$. It therefore suffices to prove that given $\config_1 \step{} \config_2$ and $\config_1' \in \perfproj{\config_1}$, there exists $\config_2' \in \perfproj{\config_1}$ such that $\config_1' \step{} \config_2'$. We denote by $s$ the step $\config_1 \step{} \config_2$; and by $s'$ the step $\config'_1 \step{} \config'_2$ that we are building. 
	Let $a \in \agents$ that performs a transition in $s$.
	\begin{itemize}
	\item If $a$ performs a local test $\loc{i_1}{i_2}{\diseqtestact}$ in $s$, then it may perform the correspondign local test in $s'$ because $\config_1' \in \perfproj{\config_1}$ hence $\config_1'(a)$ maps $i_1$ and $i_2$ to "memory slots" of distinct values. 
	\item If $a$ performs a local test  $\loc{i_1}{i_2}{\eqtestact}$, then because $\config_1'\in \perfproj{\config_1}$, it maps $i_1$ and $i_2$ to the same "memory slot" and $a$ may performs the corresponding internal transition in $\prot'$.  
	\item If $a$ performs a broadcast in $s$, then we make it perform the corresponding broadcast in $s'$. Note that, because $\config_1' \in \memoryproj{\config_1}$, the broadcasted value is the same in $s$ and $s'$. 
	\item 
	Suppose now that $a$ performs a reception $\rec{\amessage}{i}{\anact}$ in $s$. Let $\aval$ the value of the message. By above, the corresponding broadcast is performed in $s'$ with the same value $\aval$. 
		\begin{itemize}
		\item If $\anact = \quotemarks{\dummyact}$, then we make $a$ perform the corresponding transition in $s'$. 
		\item If $\anact = \quotemarks{\eqtestact}$, then if $\aval$ appears in some "memory slot" $j$ in $\config_1'$, we make $a$ perform the corresponding $\rec{\amessage}{j}{\eqtestact}$ transition in $s'$. 
		If $\aval$ does not appear in any "memory slot", then we make $a$ take the $\rec{\amessage}{j}{\enregact}$ transition with $j$ a "memory slot" that did not store the value of any register other that $i$. This case disjunction guarantees that $\config_2'(a)$ does not have twice the same value in its "memory slots", hence that $\config_2'$ is "perfect".
		\item If $\anact = \quotemarks{\diseqtestact}$, then we make $a$ perform the corresponding transition in $s'$; the disequality tests passes because, since $\config_1' \in \memoryproj{\config_1}$, the values of the "memory slots" of $i_1$ and $i_2$ in $\config_1'(a)$ are not equal.
		\end{itemize}
	\end{itemize}

	Overall, we have built $\config_2' \in \perfproj{\config_2}$ such that $\config_1' \step{} \config_2'$ in $\prot'$, which concludes the induction. We have proven that for every $\run: \config_0 \step{*} \config_f$ there exists $\run': \config_0' \step{*} \config_f'$ on $\prot'$ such that $\config_f' \in \perfproj{\config_f}$. This proves that if $q_f$ may be covered in $\prot$, then $Q_f'$ may be covered in $\prot'$. 

	Conversely, let $\run' : \config_0' \step{*} \config_f'$ a run of $\prot$ over some set of agents $\agents$. We prove that there exists a run $\run: \config_0 \step{*} \config_f$ of $\prot$ such that $\config_f' \in \memoryproj{\config_f}$. The proof is by induction on the length of $\run'$. 

	For $\run'$ of length $0$, the property is trivially satisfied. For the heredity, it suffices to prove that if we are given $\config_1' \step{} \config_2'$ and $\config_1$ such that $\config_1' \in \memoryproj{\config_1}$, then there exists $\config_2$ such that $\config_2' \in \memoryproj{\config_2}$ and $\config_1 \step{} \config_2$. The proof is similar to the previous one but simpler. Let $a$ an agent. We pick $\atrans \in \transitions$ one of the transitions in $\prot$ that, when building $\prot'$, caused the transition taken by $a$ in $\config_1' \step{} \config_2'$ to be added to $\transitions'$. A simple case disjunction allows to prove that $a$ may perform $\atrans$ from $\config_1$ (under the assumption that the broadcast value is the same, which can be easily guaranteed by looking at the broadcasting agent). Overall we obtain a step $\config_1 \step{} \config_2$ with $\config_2' \in \memoryproj{\config_2}$ by construction. This concludes the induction. We have proven that if $Q_f'$ can be covered in $\prot'$ then $q_f$ can be covered in $\prot$, hence the two properties are equivalent.
	Finally, observe that the \COVER problem without subset $Q_f' \subseteq Q'$ as objective can be converting in \COVER of a single state using internal transitions, concluding the reduction.
\end{proof}
